Supplementary Material

### 2020-12-27 docs/supplementary-information/report/report.tex
polishes docs/supplementary-information/

\documentclass[12pt]{article}
\usepackage[margin=15mm]{geometry}
\usepackage{graphicx}
\graphicspath{{../../}} %%%goes to the path: docs/

@@

\begin{abstract}
Section 1 shows surface plots of 3D RQA ENTR values for 3 participants (p01, p02 and p03).
Datasets are for 
(a) window size of 100, 250, 500 and 750 samples (w100, w250, w500, w750);
(b) smoothnes: sg0, sg1 and sg2;
(c) movement: Horizontal Normal (HN), Horizontal Faster (HF), Vertical Normal (VN) and Vertical Faster (VF); and 
(d) sensors: Sensor attached to Human (HS01), sensor attached to Robot (RS01).
\end{abstract}

@@

@@

## Data
$HOME/srep2019/data/rqa$ tree -s

@@

Datasets for NN participants where NN is 01, 02 and 03 are:
\begin{verbatim}
RQAs_pNNw100.dt
RQAs_pNNw250.dt
RQAs_pNNw500.dt
RQAs_pNNw750.dt
\end{verbatim}

>>>>

\documentclass[12pt]{article}
\usepackage[margin=15mm]{geometry}
\usepackage{graphicx}
\usepackage{url}
\graphicspath{{../../}} %%%goes to the path: docs/

@@

\begin{abstract}
Section 1 describes datasets and section 2 shows surface plots of 3D RQA ENTR values for 3 participants (p01, p02 and p03).
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Datasets}
Datasets are for 
(a) window size of 100, 250, 500 and 750 samples (w100, w250, w500, w750);
(b) smoothness: sg0, sg1 and sg2;
(c) movement: Horizontal Normal (HN), Horizontal Faster (HF), Vertical Normal (VN) and Vertical Faster (VF); and 
(d) sensors: Sensor attached to Human (HS01), sensor attached to Robot (RS01).

The location of the dataset is shown below with the first two lines of xdatav00.dt denoting labels.
\begin{verbatim}
~/srep2020/data/dataset$ tree --si
[ 46M]  xdata_v00.dt
.
.
.
"Participant" "Activity" "Sensor" "Sample" "Time" 
"sg0zmuvGyroY" "sg1zmuvGyroY" "sg2zmuvGyroY" 
"sg0zmuvGyroZ" "sg1zmuvGyroZ" "sg2zmuvGyroZ"
...
"p01" "HN" "HS01" 1 0 
0.0110396263359954 0.00606430191548277 0.0385586376765087 
0.00467559072085554 0.00509907428630649 0.168927517477539
...
\end{verbatim}

%├── [4.1k]  dataset
%│   └── [ 46M]  xdata_v00.dt
%.
%.
%.

@@

## Data
$HOME/srep2020/data/rqa$ tree -s

@@

For the following plots, datasets for NN participants where NN is 01, 02 and 03 are:
\begin{verbatim}
RQAs_pNNw100.dt
RQAs_pNNw250.dt
RQAs_pNNw500.dt
RQAs_pNNw750.dt
\end{verbatim}
